Turbulence in compact to giant HII regions

### 2022-09-20 strucfunc_paper.tex
Javier changes 2022-09-20

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity located in the Milky Way and other Local Group galaxies.
  We determine the second-order structure function of the centroid velocity two-dimensional map of the \halpha\ emission line.
  We also proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)), and the turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)).
  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters previously mentioned  with their respective confidence intervals.
  Our results are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\). 
  The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\), and that the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\), values increase following a linear monotonically relation.
  Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
  The methodology we present guarantees consistency for comparison between the galactic and giant HII regions. 
%  The second-order structure function has proved to be a useful tool to determine the existence of the correlations between random velocities and distance across the \hii{} regions.

@@

%% Will version 2021-12-07 of Intro first para (what we are studying)
Photoionized regions around high-mass stars (\hii{} regions)
show highly vigorous dynamics
as a result of the star formation process and the energy and momentum
injected by the newly-formed stars.
Rather than manifesting a simple pattern such as expansion, infall, or rotation,
the motions are frequently disordered or ``turbulent''
and must be characterised by statistical techniques.
In relatively low luminosity regions, such as the nearby Orion Nebula,
the disordered motions are approximately transonic,
with typical velocities of order \num{5} to \SI{10}{km.s^{-1}}
\citep{castaneda1988, Garcia-Diaz:2008a}.
In larger, higher luminosity regions,
such as 30~Doradus in the Large Magellanic Cloud,
the velocities are significantly supersonic,
of order \SI{30}{km.s^{-1}} \citep{Torres-Flores:2013t, Castro:2018a}.
The same tendency of increasing velocity dispersion (\(\sigma\))
and luminosity (\(L\))
continues up to the scale of entire galaxies
with an approximate relation \(L \propto \sigma^\alpha\) that spans
more than 5 orders of magnitude in luminosity
with a  power-law index \(\alpha = 3\) to~\(7\)
\citep{terlevich1981, Rozas:2006b, Chavez:2014a, Moiseev:2015a}.
However, it is not known whether a single physical mechanism
underlies this relationship at all scales.
The relative importance of gravity and the various stellar feedback mechanisms
(heating, direct radiation pressure, stellar winds, cluster winds)
are unclear in many cases and are frequently disputed \citep{Krumholz:2016a, Melnick:2021x}.

@@

% Will's 2021-12-08 new version of Intro para 4: description of our methodology
In this paper,
we employ archival data from a wide variety of integral field and multi-longslit
spectrographic datasets to analyze spatially resolved \ha{} velocity maps for a sample of
nine \hii{} regions (Figure~\ref{fig:hii-regions}),
ranging in size from \SI{0.5}{pc} to \SI{200}{pc}
and in \ha{} luminosity from \SI{e37}{erg.s^{-1}} to  \SI{e39}{erg.s^{-1}}.
The observations and the physical characteristics of our sample
are described in section~\ref{sec:HIIsample}.

We apply a uniform methodology to the analysis of the structure function
by fitting a simple functional form that consists of a power law of slope \(m\)
at small separations,
transitioning to a constant value at separations larger than
an autocorrelation length \(r_0\).
This is described in section~\ref{sec:met}.
We also take into account three observational limitations of the datasets:
the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
the finite map size, \(L_{\text{box}}\);
and a contribution of spatially uncorrelated noise, \(B_0\),
to the observed structure function.
In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
appropriate functional forms for the effects of \(s_0\), \(L_{\text{box}}\) and \(B_0\).
In our fits, we marginalize over these nuisance parameters to obtain robust
credibility limits for the parameters of astrophysical interest:
\(\sigma\pos\), \(r_0\), and \(m\).
The results of these fits are presented in section~\ref{sec:results}.

In section~\ref{sec:discussion} we discuss the relation
of our results to previous studies and the correlations that we find
between the structure function parameters and other properties of
the \hii{} regions in our sample.
%We also discuss the implications of our results for the existence of a
%Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
%for the velocity fluctuations.
Finally, in section~\ref{sec:conclusions} we present our conclusions.

@@

We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
the brightness following the southwest direction from the Huygens region.
The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky derived from spectroscopic observations are a powerful tool for studying the turbulent dynamics of emission line regions.
  With the aim to characterize these velocities fluctuations we conduct a statistical analysis on a diverse sample of 9 \hii{} regions that spans more than two orders of magnitude in size and luminosity, and are located in the Milky Way and other Local Group galaxies.
  For the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
  We proposed a heuristic model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L_{\text{box}}\)).
  The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our heuristic model.
  The observational structure function is fitted using our heuristic model in a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
  The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\). 
  Later, the derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diamater (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
  We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\). 
  Finally, the \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) relation increase following a linear relation.
  Since the derived  scale-relations are within the uncertainty of previous investigations we conclude that the parameters obtained from our proposed model represents true kinematic properties of each region.
  The methodology we present guarantees consistency for comparison between the galactic and giant extragalactic HII regions.

@@

%% Will version 2021-12-07 of Intro first para (what we are studying)
Photoionized regions around high-mass stars (\hii{} regions)
show highly vigorous dynamics
as a result of the star formation process and the energy and momentum
injected by the newly-formed stars.
Rather than manifesting a simple pattern such as expansion, infall, or rotation,
the motions are frequently disordered or ``turbulent''
and must be characterised by statistical techniques.

In relatively low luminosity regions, such as the nearby Orion Nebula,
the disordered motions are approximately transonic,
with typical velocities of order \num{5} to \SI{10}{km.s^{-1}}
\citep{castaneda1988, Garcia-Diaz:2008a}.
In larger, higher luminosity regions,
such as 30~Doradus in the Large Magellanic Cloud,
the velocities are significantly supersonic,
of order \SI{30}{km.s^{-1}} \citep{Torres-Flores:2013t, Castro:2018a}.
The same tendency of increasing velocity dispersion (\(\sigma\))
and luminosity (\(L\))
continues up to the scale of entire galaxies
with an approximate relation \(L \propto \sigma^\alpha\) that spans
more than 5 orders of magnitude in luminosity
with a  power-law index \(\alpha = 3\) to~\(7\)
\citep{terlevich1981, Rozas:2006b, Chavez:2014a, Moiseev:2015a}.
However, it is not known whether a single physical mechanism
underlies this relationship at all scales.
The relative importance of gravity and the various stellar feedback mechanisms
(heating, direct radiation pressure, stellar winds, cluster winds)
are unclear in many cases and are frequently disputed \citep{Krumholz:2016a, Melnick:2021x}.

@@

% Will's 2021-12-08 new version of Intro para 4: description of our methodology
In this paper,
we employ archival data from a wide variety of integral field and multi-longslit
spectrographic datasets to analyze spatially resolved \ha{} velocity maps for a sample of
nine \hii{} regions (Figure~\ref{fig:hii-regions}),
ranging in size from \SI{0.5}{pc} to \SI{200}{pc}
and in \ha{} luminosity from \SI{e37}{erg.s^{-1}} to  \SI{e39}{erg.s^{-1}}.
The observations and the physical characteristics of our sample
are described in section~\ref{sec:HIIsample}.
For studying the turbulence we apply a uniform methodology to the analysis of the structure function
by fitting a simple functional form that consists of a power law of slope \(m\)
at small separations,
transitioning to a constant value at separations larger than
an autocorrelation length \(r_0\).
This is described in section~\ref{sec:met}.
We also take into account three observational limitations of the datasets:
the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
the finite map size, \(L_{\text{box}}\);
and a contribution of spatially uncorrelated noise, \(B_0\),
to the observed structure function.
In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
appropriate functional forms for the effects of \(s_0\), \(L_{\text{box}}\) and \(B_0\).
In our fits, we marginalize over these nuisance parameters to obtain robust
credibility limits for the parameters of astrophysical interest:
\(\sigma\pos\), \(r_0\), and \(m\).
The results of these fits are presented in section~\ref{sec:results}.
In section~\ref{sec:discussion} we discuss the relation
of our results to previous studies and the correlations that we find
between the structure function parameters and other properties of
the \hii{} regions in our sample.
%We also discuss the implications of our results for the existence of a
%Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
%for the velocity fluctuations.
Finally, in section~\ref{sec:conclusions} we present our conclusions.

@@

We use the velocity field presented in \citet{1987A&A...176..347H} to analyze the Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}.
The EON is an extended region in southwest direction from the Huygens region which presents a diminution in the brightness.
The observational data was obtained using a Fabry-Pérot interferometer with a étalon separation of 0.5 mm on the 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of \SI{1}{arcmin} centered at \(\theta^{1}\)Ori C.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}
